VarCovar Rembrandt

### 2024-08-07 reporting/simulation_study/simu_rembrandt_breast.Rmd
reorganise and ensure reproducibility

source(file = "functions/fct_report_simu_setting.R")

dfRembrandt <- readRDS("data/rembrandt/dfresvarcovar.rds")
dfBreast <- readRDS("data/breast_cancer/dfresvarcovar.rds")
```

@@

```{r fig.height=10, fig.cap="Statistical power depending on simulation setting. N is the number of patients and NG the number of genes in the pathway. Note : scenario D, E and F do not rely on correlation matrix to simulate variance covariance matrix so the those matrix are unlikely to be positive definite."}
source("script/script_simulation/figures_simu_rembrandt_breast_v1.R")

@@

```{r fig.height=14, fig.cap="Statistical power depending on simulation setting (second batch). N is the number of patients and NG the number of genes in the pathway."}
source("script/script_simulation/figures_simu_rembrandt_breast_v2.R")

>>>>

source(file = here::here("functions/fct_report_simu_setting.R"))

dfRembrandt <- readRDS(here::here("data/rembrandt/dfresvarcovar.rds"))
dfBreast <- readRDS(here::here("data/breast_cancer/dfresvarcovar.rds"))
```

@@

```{r fig.height=10, fig.cap="Statistical power depending on simulation setting. N is the number of patients and NG the number of genes in the pathway. Note : scenario D, E and F do not rely on correlation matrix to simulate variance covariance matrix so the those matrix are unlikely to be positive definite."}
source(here::here("script/script_simulation/generate_figures/figures_simu_rembrandt_breast_v1.R"))

@@

```{r fig.height=14, fig.cap="Statistical power depending on simulation setting (second batch). N is the number of patients and NG the number of genes in the pathway."}
source(here::here("script/script_simulation/generate_figures/figures_simu_rembrandt_breast_v2.R"))
